---
toc: true
include-in-header: 
  - _includes/fontawesome.html
---

## Next meet-up

:::{.callout-note}
Please note to the change in UTC time! Since by Oct 30th, the clocks will have shifted in the UK, meet-ups over the next six months will be at **5pm UTC**. For the October meet-up, though, clocks will *not* have shifted yet in the US. 

This meet-up is on the 5th Wednesday of October (not the usual 4th).
:::

:::: {.columns}
::: {.column width="45%"}
![](images/rainbowR-next-meetup.svg)
:::

::: {.column width="10%"}
:::

::: {.column width="45%"}
**Wednesday October 30th 2024, 5pm UTC, Zoom**

```{r}
#| echo: false
#| warning: false
#| message: false
library(distilltools)
library(lubridate)
```

`r icon_link(icon = "check",
text = "register",
url = "https://us02web.zoom.us/meeting/register/tZUtdO6prj0sGdRq-hNo2neH9wV6g9NDp_fn")`

Get the time in your timezone, e.g.

```{r}
#| echo: true
ymd_hms("2024-10-30 17:00:00") |>
with_tz("Europe/Vienna")
```

```{r}
#| echo: true
ymd_hms("2024-10-30 17:00:00") |>
with_tz("America/Los_Angeles")
```

:::
::::

## Save the dates

We will have two more meet-ups in 2024:

- **[Wednesday October 30th, 5pm UTC, Zoom](https://us02web.zoom.us/meeting/register/tZUtdO6prj0sGdRq-hNo2neH9wV6g9NDp_fn)**

- Some time in the first half of December, date TBC.
  

Sign-up links will be posted here and shared via [Mastodon](https://tech.lgbt/@rainbowR){target="_blank"} and our newsletter 2-3 weeks beforehand, which you can opt-in to when you [join the community](https://docs.google.com/forms/d/1y7SOWE3IW-fpR_5Cd4mK-CMUpFZ-hvhY4cTj34JqTVE/){target="_blank"}.

## About our meetups

We hold online meetups, over Zoom. These will usually be on the the 4th Wednesday of each month, at 5pm UK time (i.e. 4pm UTC in the summer, 5pm UTC in the winter).

We usually promote meetups a couple of weeks before they take place.
The best place to hear about them is on [Mastodon](https://tech.lgbt/@rainbowR) or via our mailing list, which you can opt in to when you [join](https://docs.google.com/forms/d/1y7SOWE3IW-fpR_5Cd4mK-CMUpFZ-hvhY4cTj34JqTVE/).

These are friendly, informal gatherings, to connect with fellow community members and chat (mostly about R).

Each meetup starts with a round of introductions, followed by any updates from the rainbowR team, e.g. discussing initiatives for the group, community organisation etc.
The majority of the meetup is usually spent chatting about R. We invite participants to 'show and tell' -- they can share something related to R or Quarto. 
It could be something they're working on, or a resource/package they've found that they're enjoying using. 
It's also a chance to ask R-related questions -- there's probably someone on the call who can help! 
Of course, you don't have to show something -- there's no pressure to do so!


We require registration in advance. This helps keep the meetup safe.
