---
toc: true
include-in-header: 
  - _includes/fontawesome.html
---

## Next meet-up

:::: {.columns}
::: {.column width="45%"}
![Image with meetup details (all text in image is elsewhere in text on this page)](images/rainbowR-latest-meetup.svg)
:::

::: {.column width="10%"}
:::

::: {.column width="45%"}
**Wednesday December 17th, 2025, 4:30pm UTC, Zoom**

```{r}
#| echo: false
#| warning: false
#| message: false
library(distilltools)
library(lubridate)
```

`r icon_link(icon = "check",
text = "register",
url = "https://us02web.zoom.us/meeting/register/zhP9C3K9TY22REx_ggMejg")`

Get the time in your timezone, e.g.

```{r}
#| echo: true
library(lubridate)
ymd_hms("2025-12-17 16:30:00") |>
with_tz("Europe/Vienna")
```

```{r}
#| echo: true
ymd_hms("2025-12-17 16:30:00") |>
with_tz("America/Los_Angeles")
```

:::
::::

## Future meet-ups

We hold online meetups, over Zoom. These will usually be on the last Wednesday of each month, at 4:30pm UK time (i.e. 3:30pm UTC in the summer, 4:30pm UTC in the winter).

::: {.callout-note}
Note that for the Winter 2025/26 series, we have moved the meet-ups **30 minutes later relative to UTC time** than the Summer 2025 series. This largely has this has the effect of making the meet-ups **30 minutes earlier**, once your country comes out of daylight savings time. In the UK and Europe, that holds for the whole series. Depending on when clocks change in your country, the October 2025 and/or March 2026 meet-ups might be **30 minutes later** (this is the case, for example, for those in Pacific time).

Note also that the December meet-up is on the 17th (the 3rd Wednesday of the month), to avoid clashes with Christmas and New Year.
:::

We schedule the meet-ups as recurring Zoom meetings, with separate registration links for winter and summer series. The series switch when the clocks change in the UK. You only need to register once per series, and you'll get a calendar invitation for all the meet-ups in that series (though of course no requirement to come to all of them!).

### Winter 2025/26 series (4:30pm UTC)

`r icon_link(icon = "check",
text = "register for the winter series",
url = "https://us02web.zoom.us/meeting/register/zhP9C3K9TY22REx_ggMejg")`

- Wednesday, **October 29th**, 4:30pm UTC, Zoom
- Wednesday, **November 26th**, 4:30pm UTC, Zoom
- Wednesday, **December 17th**, 4:30pm UTC, Zoom
- Wednesday, **January 28th**, 4:30pm UTC, Zoom
- Wednesday, **February 25th**, 4:30pm UTC, Zoom
- Wednesday, **March 25th**, 4:30pm UTC, Zoom

Details will also be shared via [Mastodon](https://tech.lgbt/@rainbowR){target="_blank"}, [Bluesky](https://bsky.app/profile/rainbowr.org), [LinkedIn](https://www.linkedin.com/company/rainbowr/) and our newsletter^[You can opt-in to the newsletter when you [join the community](https://docs.google.com/forms/d/1y7SOWE3IW-fpR_5Cd4mK-CMUpFZ-hvhY4cTj34JqTVE/){target="_blank"}.] in the run-up to each meet-up.

## About our meet-ups

We usually promote meetups a couple of weeks before they take place.
The best place to hear about them is on [Mastodon](https://tech.lgbt/@rainbowR), [Bluesky](https://bsky.app/profile/rainbowr.org), [LinkedIn](https://www.linkedin.com/company/rainbowr) or via our mailing list, which you can opt in to when you [join](https://docs.google.com/forms/d/1y7SOWE3IW-fpR_5Cd4mK-CMUpFZ-hvhY4cTj34JqTVE/).

These are friendly, informal gatherings, to connect with fellow community members and chat (mostly about R).

Each meetup starts with a round of introductions, followed by any updates from the rainbowR team, e.g. discussing initiatives for the group, community organisation etc.
The majority of the meetup is usually spent chatting about R. We invite participants to 'show and tell' -- they can share something related to R or Quarto.
It could be something they're working on, or a resource/package they've found that they're enjoying using.
It's also a chance to ask R-related questions -- there's probably someone on the call who can help!
Of course, you don't have to show something -- there's no pressure to do so!

We require registration in advance. This helps keep the meetup safe.
